### 2024-02-22 README.Rmd
reorganise folders

  - [:file\_folder: data](/data): Data used in the analysis.
  - [:file\_folder: figures](/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplements](/supplements):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder:
    source_data](/source_data):
    Source data files associated with each figure containing all data points that have been plotted in the figure.

>>>>

  - [:file\_folder: data](analysis/data): Data used in the analysis.
  - [:file\_folder: data](analysis/scripts): scripts used in the analysis.
  - [:file\_folder: figures](manuscript/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplements](manuscript/supplements):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder:
    source_data](/manuscript/source_data):
    Source data files associated with each figure containing all data points that have been plotted in the figure.
